\newglossaryentry{cas}{
 % how the entry name should appear in the glossary
name={computer algebra system (CAS)},
 % how the description should appear in the glossary
 % I have to protect fragile commands
description={A computer program the performs symbolic operations},
 % how the entry should appear in the document text
text={CAS},
 % how the entry should appear the first time it is
 % used in the document text
first={computer algebra system (CAS)}}

\newglossaryentry{integration}{
name={integration},
description={One of two fundamental operations in \gls{calculus} (the
other being differentiation).  Integration deals with the area under
curves.  Informally, $\int_a^b{f(x)\,dx}$ represents the area under the
curve defined by the function $f(x)$ from the points $x=a$ to $x=b$.  It
is an important result from \gls{calculus} called the Fundamental
Theorem of Calculus that integration and \Antidifferentiation, the
inverse operation of \gls{differentiation}, are essentially the same
thing}
}

\newglossaryentry{calculus}{
name={calculus},
description={The branch of mathematics that studies limits, derivatives,
integrals, and infinite series.  Informally, calculus is the study of
change.  Calculus is one of the most applied branch of mathematics; it
is used in every single branch of the physical sciences}
}

\newglossaryentry{differentiation}{
name={differentiation},
description={One of two fundamental operations in \gls{calculus} (the
other being integration).  Differentiation deals with the change of
functions.  The function $\frac{df}{dx}$ is called the derivative of
$f$, and it informally represents the change, or slope, of the function
$f$ at any point $x$.  $\frac{df}{dx}$ is also sometimes denoted as
$f'(x)$, or simply $f'$ when the the independent variable $x$ is clear}
}

\newglossaryentry{elementary}{
name={elementary},
description={Roughly speaking, a function is elementary if it can be
represented as a combination of exponentials, logarithms, powers, and
trigonometric functions by addition, subtraction, multiplication,
division, and composition. For example, $\frac{\sin{(x^2 +
1)}}{\sqrt[3]{\ln{x}}}$ is elementary, but
$\frac{2}{\sqrt{\pi}}\int{e^{-x^2}\,dx}$, the \gls{error function}, is
not. See Bronstein's book \cite{bronstein2005symbolic}, page 133, for a
more rigorous definition}
}

\newglossaryentry{error function}{
name={error function},
description={The function defined by \[\mathrm{erf}{(x)} =
\frac{2}{\sqrt{\pi}}\int{e^{-x^2}\,dx}.\]  This is the classic example
of an integral of an \gls{elementary} function that is not itself
\gls{elementary}.  The \gls{error function} is important in statistics.
In particular, it represents the cumulative distribution function of the
normal distribution (i.e., a bell curve), and its values are used to
calculate probabilities.  The fact that this function is non-elementary
implies that statistical computing packages must use numerical
techniques to calculate these values, as it does not have a closed form
solution}
}

\newglossaryentry{transcendental}{
name={transcendental},
description={A function is \gls{transcendental} if it is not
\gls{algebraic}.  A function is \textit{purely \gls{transcendental}} if
it does not contain any \gls{algebraic} components.  An important result
from analysis is that the functions $e^x$, $\ln{x}$, $\sin{x}$,
$\cos{x}$, and $\tan{x}$ are all \gls{transcendental}.  Roughly
speaking, a function is \gls{transcendental} if it contains one of
these, and it is purely \gls{transcendental} if it does not contain any
radicals.
%\footnote{There are exceptions to this rule.  For example,
%$e^{\frac{1}{2}\ln{x}}$ is not transcendental because it is equivalent to
%$\sqrt{x}$.  An important part of the \gls{transcendental} part of the
%Risch Algorithm involves making sure that the integrand really is
%\gls{transcendental}}  
For example, $e^{x + 1}$ is purely
\gls{transcendental}, $\sqrt[3]{\ln{x}}$ is \gls{transcendental} but not
purely \gls{transcendental}, and $\sqrt{x}$ is neither
\gls{transcendental} nor purely \gls{transcendental} (it is
\gls{algebraic})}
}

\newglossaryentry{algebraic}{
name={algebraic},
description={A function is \gls{algebraic} if it is the root of a
polynomial with coefficients that are rational functions with rational
number coefficients.  For example, the function $\sqrt{x + 1}$ is
\gls{algebraic} because it is the root of the polynomial $y^2 = x + 1$. 
A function that is not \gls{algebraic} is called \gls{transcendental}}
}

\newglossaryentry{integrand}{
name={integrand},
description={The argument of an integral.  For example, the
\gls{integrand} of $\int{\sin{x}\,dx}$ is $\sin{x}$}
}

\newglossaryentry{rational function}{
name={rational function},
description={Any function that can be written as polynomial divided by a
polynomial.  For example, $\frac{x^2 + 1}{x^3 - x}$ is a \gls{rational
function}}
}
