\renewcommand{\thefootnote}{\fnsymbol{footnote}}	
The following are some classic examples of integrals of \gls{transcendental}
\gls{elementary} functions that do not have closed form (\gls{elementary})
solutions.

\begin{equation}
\label{erf}
\int{e^{-x^2}\,dx};
\end{equation}
\begin{equation}
\label{exp_x_squared}
\int{e^{x^2}\,dx};
\end{equation}
\begin{equation}
\label{li}
\int{\frac{1}{\ln{x}}\,dx};
\end{equation}
\begin{equation}
\label{x_to_the_x}
\int{x^x\,dx};
\end{equation}
\begin{equation}
\label{x_to_the_neg_x}
\int{x^{-x}\,dx};
\end{equation}
\begin{equation}
\label{Si}
\int{\frac{\sin{x}}{x}\,dx};
\end{equation}
\begin{equation}
\label{Ci}
\int{\frac{\cos{x}}{x}\,dx};
\end{equation}
\begin{equation}
\label{exp_x_ln_x}
\int{e^x\ln{x}\,dx}
\end{equation}

\textbf{Notes}
\begin{itemize}
\item Integral \ref{erf} is, except for a constant factor, the
\gls{error function}.  See the Glossary.
\item Integral \ref{li} is is often denoted by $\mathrm{li}(x)$
(Logarithmic Integral).
\item The integrals \ref{Si} and \ref{Ci} are often denoted by
$\mathrm{Si}(x)$ (Sine Integral) and $\mathrm{Ci}(x)$ (Cosine Integral),
respectively.  Similar integrals with $e^x$, $\cosh{x}$, and $\sinh{x}$
are also nonelementary and have corresponding named special functions.
\item Integrals \ref{erf}, \ref{exp_x_squared}, \ref{li},
\ref{x_to_the_x}, \ref{x_to_the_neg_x}, and \ref{exp_x_ln_x}, as well as
the additional integrals noted in the previous bullet point, can all be
proved to be nonelementary using \rischintegrate{}.
The remaining integrals are trigonometric and hence not implemented yet
(see Section \ref{future}).  However, the fact that they are not
\gls{elementary} is can be shown by applying the relevant part of the Risch
Algorithm to them. For example, the steps  for integral \ref{Si} are
worked out in in Bronstein's book~\cite{bronstein2005symbolic}, page 169.
\item There are many classic nonelementary integrals of
non-\gls{transcendental} \gls{elementary} functions, such as the hyperbolic
integrals.  We do not look at these here, as the focus of this paper is
chiefly on the \gls{transcendental} part of the Risch Algorithm.
\end{itemize}